\documentclass{article}


\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries}
{$\bullet$}
{1em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}

\titlespacing{\subsection}{0em}{.25em}{0em}


\renewcommand{\maketitle}{
\begin{center}
{\LARGE\bfseries
\theauthor}

\vspace{0.25em}
\href{mailto:vdharam18@gmail.com}{vdharam18@gmail.com} --- \href{http://vdharam.com}{http://vdharam.com}
\end{center}	
}




\begin{document}
\title{Resume}
\author{Dharmendra Lalji Vishwakarma}
\maketitle

\section{Profile:}
\begin{itemize}
\itemsep0em
\item[$\bullet$]
Senior software engineer with 5 years and 2 months of solid experience in enterprise web application development using technologies Java, J2EE, Spring, Hibernate, Angular, Grails and ZK.
\item[$\bullet$]
Practical experience of a building project from scratch.
\item[$\bullet$]
Finance domain application development expertise in terms of application security, integration and automation.
\item[$\bullet$]
Pursuing a Master's in Data Analytics from National College of Ireland for better career prospects.
\item[$\bullet$]
Available for part-time/remote projects during the term and full-time opportunities from June 2019.
\item[$\bullet$]
Seeking opportunity in Software Development
\end{itemize}
\section{Education:}
\textbf{09.2018 – 09.2019 \hfill National College of Ireland, Dublin\\}
\underline{MSc in Data Analytics} \hfill \href{www.ncirl.ie}{www.ncirl.ie}\\
\textbf{Modules:} Statistics for Data Analytics, Data Storage \& Management, Data warehouse \& business intelligence, Strategic ICT \& eBusiness Implementation, Advanced Data Mining, Data Visualization, Research in Computing, Programming for Data Analytics and Research Project.\hfill\\
\linebreak
\textbf{07.2009 – 05.2013 \hfill St. Francis Institute of Technology, Mumbai\\}
\underline{B.E. in Information Technology (Grade :72.47\%)} \hfill \href{www.sfitengg.org}{www.sfitengg.org} \\
\textbf{Modules:} Data structure and Algorithms, Operating Systems, Computer Networks, Object-Oriented Programming, Databases, Software Engineering, Internet Programming, Applied and Computational Mathematics.\hfill\\
\linebreak
\textbf{06.2007 – 06.2009 \hfill Shailendra Education Society, Mumbai \\}
\underline{H.S.C (Grade :83.67\%)} \hfill \href{www.shailendradegreecollege.in}{www.shailendradegreecollege.in}

\section{Technology Skills:}
\subsection{Programming Languages:}
Java, J2EE, SQL, PL-SQL, JSP, Servlets, ORACLE, MySQL, HTML, JavaScript, jQuery.
\subsection{Frameworks:}
 Spring, Hibernate, Grails, ZK, Angular JS, Angular 4, Liferay portlets JSR 286.
\subsection{Tools \& Others:} Eclipse, GGTs, Net beans, Centos Server, AutoSys, Bash, SVN, Git, Apache Tomcat, Glassfish Server, Magic-XPI, Basic Hardware \& Networking Knowledge.
\subsection{Course \& Certification:}
Oracle Certified Associate Oracle 11g DBA (SQL fundamental-1), Corporate Training

\section{Career History:}
\textbf{10.2017- 08.2018: \hfill Larsen \& Toubro Infotech, India \\}
\underline{Senior Software Engineer} \hfill \href{www.lntinfotech.com}{www.lntinfotech.com}
\begin{itemize}
	\itemsep0em
	\item Worked in a product development team of client Citi, MONET project.
	\begin{itemize}
		\itemsep0em
		\item Collaborated with existing team to understand requirements and implemented new features on the product.
		\item Analysed the reporting framework of the existing application to propose further enhancements.
		\item Automated the flow of application data Management from upstream systems. This has led to a significant boost in the process as compared to the manual work.
		\item Supported the team for Sprint releases.
	\end{itemize}
	\item \textbf{Technology and Platform:} Java, Spring, GWT, Hibernate, Angular 4 (for new dashboards), Oracle Database, AutoSys, MongoDB (Archiving), JBoss, Linux.
	\item Worked on a microservices architecture based prototype application with Spring Boot and Java and helped the team of developers for implementing in a new system.

\end{itemize}
\textbf{03.2016-10.2017: \hfill Intelliswift Software India Pvt Ltd, India\\}
\underline{Senior Software Engineer} \hfill \href{www.intelliswift.co.in}{www.intelliswift.co.in}
\begin{itemize}
	\itemsep0em
\item Developed 3 web products from scratch for the banking domain.
\item Followed OWASP points for application security, role-based \& maker-checker based admin system.
\item Implemented system integration workflow design with the fail-over mechanism.
\item Performed tuning of application time-to-time on development builds to ensure the optimum performance (with Sonar-lint, PMD, GTmetrix, New Relic and App dynamics).
\item Provided UAT/Production support to the client at Offshore/Onsite.
\item \textbf{Technology and Platform:} Java, Spring, Hibernate, Oracle Database, JavaScript, jQuery, Apache Tomcat, Linux.
\end{itemize}
\textbf{10.2015- 02.2016: \hfill Freelancing\\}
\underline{Freelance Developer}
\begin{itemize}
	\itemsep0em
	\item Mentored and developed a web app for a client as per the specification.
	\item Worked as a freelance teacher for Java and Data structure \& Algorithms.
	\item Built a portfolio site vdharam.com to showcase the skills considering the enterprise development standards.
\end{itemize}
\textbf{07.2013- 02.2015: \hfill Neebal Technologies Pvt Ltd, India \\}
\underline{Software Engineer} \hfill \href{www.neebal.com}{www.neebal.com}
\begin{itemize}
	\itemsep0em
	\item Developed 10+ projects with different clients and guided a team of developers for code quality and performance in an agile environment.
	\item Managed the company’s major client projects single-handedly and suggested technical improvements.
	\item Successfully launched client’s major system upgrade keeping the current system live.
	\item Attended corporate training and mastered the skill for java application development, reporting, optimisation and scalability.
	\item \textbf{Technology and Platform:} Java, Grails, ZK, Spring, Hibernate, Angular, JavaScript, jQuery, Oracle, MySQL, ActiveMQ, Magic XPI, Glassfish Server, Apache Tomcat, CentOS.
\end{itemize}

\section{Interests and Achievements}
\subsection{Own Projects:}
As a passionate developer, I maintain \href{www.vdharam.com}{www.vdharam.com} and \href{http://vdharam.wordpress.com}{http://vdharam.wordpress.com}.
\subsection{Work Achievements:}
Neebal Excellence award for a successful product launch.

\section{}
\bfseries
Stamp 2 visa: Eligible to work 20 hours a week during term time, 40 hours a week during holidays.

\end{document}